04_LDA_v2

### 2019-12-25 analysis/04_LDA.Rmd
now with sex as a class

  df <- read.csv(pathtofile, row.names = 1)
  savecols <- as.character(colData$V1) 
  savecols <- as.vector(savecols) 
  df <- df %>% dplyr::select(one_of(savecols)) 
  df <- as.data.frame(t(df))
  df$V1 <- row.names(df)
  return(df)
}

@@

  train.data <- left_join(trainsamples, traindata) %>%
    dplyr::select(-V1, -bird, -tissue, -group, -study, -sex)

  test.data <- testdata

@@

  # LDA analysis
  # Fit the model
  model <- lda(treatment~ ., data = train.transformed)
  # Make predictions
  predictions <- model %>% predict(test.transformed)

  # Model accuracy
  print("model accuracy")
  print("predictions$class==test.transformed$treatment)")
  print(mean(predictions$class==test.transformed$treatment))

@@

```{r LDAplots}
library(kableExtra)

@@

```{r LDApredictions}

>>>>

  df <- read.csv(pathtofile, row.names = 1)
  savecols <- as.character(colData$V1) 
  savecols <- as.vector(savecols) 
  df <- df %>% dplyr::select(one_of(savecols))

  # keep only 100 genes fornow
  #df <- head(df, 100)

  df <- as.data.frame(t(df))
  df$V1 <- row.names(df)
  return(df)
}

@@

  train.data <- left_join(trainsamples, traindata) %>%
    dplyr::select(-V1, -bird, -tissue, -group, -study)

  test.data <- left_join(testsamples, testdata) %>%
    dplyr::select(-V1, -bird, -tissue, -group, -study, -treatment)

  testsamples <- testsamples

@@

  # LDA analysis
  # Fit the model
  model <- lda(treatment ~ ., data = train.transformed)
  # Make predictions
  predictions <- model %>% predict(test.transformed)

  # Model accuracy
  print("model accuracy")
  #print("predictions$class==test.transformed$treatment)")
 # print(mean(predictions$class==test.transformed$treatment))

@@

```{r LDAplots}

@@

```{r LDApredictions}
library(kableExtra)

### 2019-12-25 analysis/04_LDA_v2.Rmd
now with sex as a class

  train.data <- left_join(trainsamples, traindata) %>%
    dplyr::select(-V1, -bird, -tissue, -group, -study, -sex, -treatment)

>>>>

  train.data <- left_join(trainsamples, traindata) %>%
    dplyr::select(-V1, -bird, -tissue, -group, -study, - treatment)

  test.data <- left_join(testsamples, testdata) %>%
    dplyr::select(-V1, -bird, -tissue, -group, -study, -treatment,  -newgrouping)
